Creating Supplementary Table of all Performances

### 2019-05-16 Scripts/creating_supplementary_table_of_all_performances.Rmd
editted results script

```{r}
#OC
##None
rfperf_gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_10kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##None
rfperf_gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_25kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##None
rfperf_gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_50kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##None
rfperf_gm12878_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_100kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_gm12878_10kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_gm12878_10kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_gm12878_10kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_gm12878_25kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_gm12878_25kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_gm12878_25kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_gm12878_50kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_gm12878_50kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_gm12878_50kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_gm12878_100kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_gm12878_100kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_gm12878_100kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_gm12878_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_gm12878_10kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_gm12878_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_gm12878_25kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_gm12878_25kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_gm12878_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_gm12878_50kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_gm12878_50kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_gm12878_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_gm12878_100kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_gm12878_100kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_gm12878_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

#OC
##SMOTE
rfperf_gm12878_10kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##SMOTE
rfperf_gm12878_10kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##SMOTE
rfperf_gm12878_10kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

#OC
##SMOTE
rfperf_gm12878_25kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##SMOTE
rfperf_gm12878_25kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##SMOTE
rfperf_gm12878_25kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

#OC
##SMOTE
rfperf_gm12878_50kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##SMOTE
rfperf_gm12878_50kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##SMOTE
rfperf_gm12878_50kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

#OC
##SMOTE
rfperf_gm12878_100kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##SMOTE
rfperf_gm12878_100kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##SMOTE
rfperf_gm12878_100kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

#OC
##None
rfperf_K562_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_K562_10kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_K562_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##None
rfperf_K562_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_K562_25kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_K562_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##None
rfperf_K562_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_K562_50kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_K562_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##None
rfperf_K562_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_K562_100kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_K562_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_K562_10kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_K562_10kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_K562_10kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_K562_25kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_K562_25kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_K562_25kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_K562_50kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_K562_50kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_K562_50kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_K562_100kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_K562_100kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_K562_100kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_K562_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_K562_10kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_K562_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_K562_25kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_K562_25kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_K562_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_K562_50kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_K562_50kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_K562_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_K562_100kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_K562_100kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_K562_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

#OC
##SMOTE
rfperf_K562_10kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##SMOTE
rfperf_K562_10kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##SMOTE
rfperf_K562_10kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

#OC
##SMOTE
rfperf_K562_25kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##SMOTE
rfperf_K562_25kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##SMOTE
rfperf_K562_25kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

#OC
##SMOTE
rfperf_K562_50kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##SMOTE
rfperf_K562_50kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##SMOTE
rfperf_K562_50kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

#OC
##SMOTE
rfperf_K562_100kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##SMOTE
rfperf_K562_100kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##SMOTE
rfperf_K562_100kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

@@

# Creating and saving table with all results

```{r}
all_rfperfs_df <- rbind.data.frame(rfperf_gm12878_10kb_none_oc,
                                   rfperf_gm12878_10kb_none_op,
                                   rfperf_gm12878_10kb_none_dist,
                                   rfperf_gm12878_25kb_none_oc,
                                   rfperf_gm12878_25kb_none_op,
                                   rfperf_gm12878_25kb_none_dist,
                                   rfperf_gm12878_50kb_none_oc,
                                   rfperf_gm12878_50kb_none_op,
                                   rfperf_gm12878_50kb_none_dist,
                                   rfperf_gm12878_100kb_none_oc,
                                   rfperf_gm12878_100kb_none_op,
                                   rfperf_gm12878_100kb_none_dist,

                                   rfperf_gm12878_10kb_ROS_oc,
                                   rfperf_gm12878_10kb_ROS_op,
                                   rfperf_gm12878_10kb_ROS_dist,
                                   rfperf_gm12878_25kb_ROS_oc,
                                   rfperf_gm12878_25kb_ROS_op,
                                   rfperf_gm12878_25kb_ROS_dist,
                                   rfperf_gm12878_50kb_ROS_oc,
                                   rfperf_gm12878_50kb_ROS_op,
                                   rfperf_gm12878_50kb_ROS_dist,
                                   rfperf_gm12878_100kb_ROS_oc,
                                   rfperf_gm12878_100kb_ROS_op,
                                   rfperf_gm12878_100kb_ROS_dist,

                                   rfperf_gm12878_10kb_RUS_oc,
                                   rfperf_gm12878_10kb_RUS_op,
                                   rfperf_gm12878_10kb_RUS_dist,
                                   rfperf_gm12878_25kb_RUS_oc,
                                   rfperf_gm12878_25kb_RUS_op,
                                   rfperf_gm12878_25kb_RUS_dist,
                                   rfperf_gm12878_50kb_RUS_oc,
                                   rfperf_gm12878_50kb_RUS_op,
                                   rfperf_gm12878_50kb_RUS_dist,
                                   rfperf_gm12878_100kb_RUS_oc,
                                   rfperf_gm12878_100kb_RUS_op,
                                   rfperf_gm12878_100kb_RUS_dist,

                                   rfperf_gm12878_10kb_SMOTE_oc,
                                   rfperf_gm12878_10kb_SMOTE_op,
                                   rfperf_gm12878_10kb_SMOTE_dist,
                                   rfperf_gm12878_25kb_SMOTE_oc,
                                   rfperf_gm12878_25kb_SMOTE_op,
                                   rfperf_gm12878_25kb_SMOTE_dist,
                                   rfperf_gm12878_50kb_SMOTE_oc,
                                   rfperf_gm12878_50kb_SMOTE_op,
                                   rfperf_gm12878_50kb_SMOTE_dist,
                                   rfperf_gm12878_100kb_SMOTE_oc,
                                   rfperf_gm12878_100kb_SMOTE_op,
                                   rfperf_gm12878_100kb_SMOTE_dist,

                                   rfperf_K562_10kb_none_oc,
                                   rfperf_K562_10kb_none_op,
                                   rfperf_K562_10kb_none_dist,
                                   rfperf_K562_25kb_none_oc,
                                   rfperf_K562_25kb_none_op,
                                   rfperf_K562_25kb_none_dist,
                                   rfperf_K562_50kb_none_oc,
                                   rfperf_K562_50kb_none_op,
                                   rfperf_K562_50kb_none_dist,
                                   rfperf_K562_100kb_none_oc,
                                   rfperf_K562_100kb_none_op,
                                   rfperf_K562_100kb_none_dist,

                                   rfperf_K562_10kb_ROS_oc,
                                   rfperf_K562_10kb_ROS_op,
                                   rfperf_K562_10kb_ROS_dist,
                                   rfperf_K562_25kb_ROS_oc,
                                   rfperf_K562_25kb_ROS_op,
                                   rfperf_K562_25kb_ROS_dist,
                                   rfperf_K562_50kb_ROS_oc,
                                   rfperf_K562_50kb_ROS_op,
                                   rfperf_K562_50kb_ROS_dist,
                                   rfperf_K562_100kb_ROS_oc,
                                   rfperf_K562_100kb_ROS_op,
                                   rfperf_K562_100kb_ROS_dist,

                                   rfperf_K562_10kb_RUS_oc,
                                   rfperf_K562_10kb_RUS_op,
                                   rfperf_K562_10kb_RUS_dist,
                                   rfperf_K562_25kb_RUS_oc,
                                   rfperf_K562_25kb_RUS_op,
                                   rfperf_K562_25kb_RUS_dist,
                                   rfperf_K562_50kb_RUS_oc,
                                   rfperf_K562_50kb_RUS_op,
                                   rfperf_K562_50kb_RUS_dist,
                                   rfperf_K562_100kb_RUS_oc,
                                   rfperf_K562_100kb_RUS_op,
                                   rfperf_K562_100kb_RUS_dist,

                                   rfperf_K562_10kb_SMOTE_oc,
                                   rfperf_K562_10kb_SMOTE_op,
                                   rfperf_K562_10kb_SMOTE_dist,
                                   rfperf_K562_25kb_SMOTE_oc,
                                   rfperf_K562_25kb_SMOTE_op,
                                   rfperf_K562_25kb_SMOTE_dist,
                                   rfperf_K562_50kb_SMOTE_oc,
                                   rfperf_K562_50kb_SMOTE_op,
                                   rfperf_K562_50kb_SMOTE_dist,
                                   rfperf_K562_100kb_SMOTE_oc,
                                   rfperf_K562_100kb_SMOTE_op,
                                   rfperf_K562_100kb_SMOTE_dist)

all_rfperfs_df$CellLine <- c(rep("GM12878",19*48),rep("K562",19*48))
all_rfperfs_df$Resolution <- rep(c(rep("10 kb", 19*3),rep("25 kb", 19*3),rep("50 kb", 19*3),rep("100 kb", 19*3)),8)
all_rfperfs_df$Resampling <- rep(c(rep("None",19*12),rep("ROS",19*12),rep("RUS",19*12),rep("SMOTE",19*12)), 2)
all_rfperfs_df$PredictorType <- rep(c("OC", "OP", "Distance"),19*32)

all_rfperfs_df <- all_rfperfs_df[,c(3,4,5,6,1,2)]
all_rfperfs_df$Performance <- round(all_rfperfs_df$Performance, 3)

write.csv(all_rfperfs_df, "C:/Users/stili/Downloads/table3_all_model_performances.csv")
```

>>>>

## GM12878

```{r}
rfperf_metric <- as.character()
rfperf_chr <- as.character()
rfperf_res <- as.character()
rfperf_samp <- as.character()
rfperf_pred <- as.character()
rfperf_perf <- as.numeric()

for(i in c("10kb", "25kb", "50kb", "100kb")){
  for(j in paste0("CHR", c(1:8,10:22))){
    for(k in c("none", "ros", "rus", "smote")){
      for(l in c("oc","op","distance")){
        perfdat <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/",
                                 i,
                                 "/results_by_chr/",
                                 j,
                                 "/",
                                 k,
                                 "/",
                                 l,
                                 "/enet/rfperf.rds"))

        rfperf_res <- c(rfperf_res, rep(i,8))
        rfperf_chr <- c(rfperf_chr,rep(j,8))
        rfperf_samp <- c(rfperf_samp,rep(k,8))
        rfperf_pred <- c(rfperf_pred,rep(l,8))
        rfperf_metric <- c(rfperf_metric, as.character(perfdat$Metric[c(6,7,9,10,15:17,19)]))
        rfperf_perf <- c(rfperf_perf, perfdat$Performance[c(6,7,9,10,15:17,19)])

      }
    }
  }
}

gm12878_all_perfs <- cbind.data.frame(rfperf_res, rfperf_chr, rfperf_samp, rfperf_pred, rfperf_metric, rfperf_perf)
colnames(gm12878_all_perfs) <- c("Resolution", "CHR", "Resampling", "Predictor", "Metric", "Performance")

gm12878_all_perfs$Resolution <- factor(gm12878_all_perfs$Resolution, levels=c("10kb","25kb","50kb","100kb"))
gm12878_all_perfs$CHR <- factor(gm12878_all_perfs$CHR, levels=paste0("CHR", c(1:8,10:22)))
gm12878_all_perfs$Resampling <- factor(gm12878_all_perfs$Resampling, levels=c("none", "ros", "rus", "smote"))
gm12878_all_perfs$Predictor <- factor(gm12878_all_perfs$Predictor, levels=c("oc","op","distance"))
gm12878_all_perfs$Metric <- factor(gm12878_all_perfs$Metric, levels=c("Sensitivity", "Specificity", "Accuracy", "Precision", "MCC", "F1", "AUC", "AUPRC"))

gm12878_all_perfs_summ <- gm12878_all_perfs %>%
  group_by(Resolution, Resampling, Predictor, Metric) %>%
  dplyr::summarise(AvePerf = mean(Performance, na.rm = TRUE),
            SDPerf = sd(Performance, na.rm = TRUE))

gm12878_all_perfs_summ$AvePerf <- round(gm12878_all_perfs_summ$AvePerf, 3)
gm12878_all_perfs_summ$SDPerf <- round(gm12878_all_perfs_summ$SDPerf, 3)

@@

## K562

```{r}
rfperf_metric <- as.character()
rfperf_chr <- as.character()
rfperf_res <- as.character()
rfperf_samp <- as.character()
rfperf_pred <- as.character()
rfperf_perf <- as.numeric()

for(i in c("10kb", "25kb", "50kb", "100kb")){
  for(j in paste0("CHR", c(1:8,10:22))){
    for(k in c("none", "ros", "rus", "smote")){
      for(l in c("oc","op","distance")){
        perfdat <- readRDS(paste0("Z:/TAD_data_analysis/K562/",
                                 i,
                                 "/results_by_chr/",
                                 j,
                                 "/",
                                 k,
                                 "/",
                                 l,
                                 "/enet/rfperf.rds"))

        rfperf_res <- c(rfperf_res, rep(i,8))
        rfperf_chr <- c(rfperf_chr,rep(j,8))
        rfperf_samp <- c(rfperf_samp,rep(k,8))
        rfperf_pred <- c(rfperf_pred,rep(l,8))
        rfperf_metric <- c(rfperf_metric, as.character(perfdat$Metric[c(6,7,9,10,15:17,19)]))
        rfperf_perf <- c(rfperf_perf, perfdat$Performance[c(6,7,9,10,15:17,19)])

      }
    }
  }
}

K562_all_perfs <- cbind.data.frame(rfperf_res, rfperf_chr, rfperf_samp, rfperf_pred, rfperf_metric, rfperf_perf)
colnames(K562_all_perfs) <- c("Resolution", "CHR", "Resampling", "Predictor", "Metric", "Performance")

K562_all_perfs$Resolution <- factor(K562_all_perfs$Resolution, levels=c("10kb","25kb","50kb","100kb"))
K562_all_perfs$CHR <- factor(K562_all_perfs$CHR, levels=paste0("CHR", c(1:8,10:22)))
K562_all_perfs$Resampling <- factor(K562_all_perfs$Resampling, levels=c("none", "ros", "rus", "smote"))
K562_all_perfs$Predictor <- factor(K562_all_perfs$Predictor, levels=c("oc","op","distance"))
K562_all_perfs$Metric <- factor(K562_all_perfs$Metric, levels=c("Sensitivity", "Specificity", "Accuracy", "Precision", "MCC", "F1", "AUC", "AUPRC"))

K562_all_perfs_summ <- K562_all_perfs %>%
  group_by(Resolution, Resampling, Predictor, Metric) %>%
  dplyr::summarise(AvePerf = mean(Performance, na.rm = TRUE),
            SDPerf = sd(Performance, na.rm = TRUE))

K562_all_perfs_summ$AvePerf <- round(K562_all_perfs_summ$AvePerf, 3)
K562_all_perfs_summ$SDPerf <- round(K562_all_perfs_summ$SDPerf, 3)
